---
title: "Boots on the Ground"
output:
  html_document:
    toc: false
editor_options: 
  markdown: 
    wrap: 72
---
```{r, include=FALSE}
 
library("here")
 library("knitr")
library("dplyr")
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,fig.align="left"  )
```

This is a 3-year interdisciplinary and collaborative regional project
co-directed by the University of Wisconsin-Madison and The Pennsylvania
State University, with collaborators in OH, MI, IA, MN, NE, and ND. The
primary goal of the project is to analyze farmer data (yield, management
practices and associated costs) in fields located across the
North-Central US. Our primary focus is on increased profitability
through improved knowledge of yield-limiting factors and best management
practices.
There are two major segments of this project:
  
-    The **Production survey** is available
    [here](https://survey123.arcgis.com/share/4bacfb5607d147ac80c2fe282ad7206a) and **checklist** of info necessary 
    to fill in the guide is [here](https://docs.google.com/document/d/1I1oa36d_ObWw13RJOL4bM_ONlPZi4OWQMujQPUF7BQo/edit?usp=sharing)
 

-    Intensive field scouting across several states (more info
    [here](https://coolbean.info/soybean-research/data-driven-knowledge/)) and the **How to** guide is [here](https://docs.google.com/document/d/1I1oa36d_ObWw13RJOL4bM_ONlPZi4OWQMujQPUF7BQo/edit?usp=sharing)
    

```{=html}

<div style="width: 640px; height: 480px; margin: 10px; position: relative;"><iframe allowfullscreen frameborder="0" style="width:640px; height:480px" src="https://lucid.app/documents/embedded/02e6e129-1594-4ccf-b774-677a981fedca" id="kbUg_0~mFnz0"></iframe></div>
```

Please send any queries to mladen@psu.edu   
All data collected for this project will be kept strictly confidential.
 
