---
title: "Boots on the Ground"
output:
  html_document:
    toc: false
editor_options: 
  markdown: 
    wrap: 72
---
```{r, include=FALSE}
 
library("here")
 library("knitr")
library("dplyr")
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,fig.align="left"  )
```
# Test
This is a 3-year interdisciplinary and collaborative regional project
co-directed by the University of Wisconsin-Madison and The Pennsylvania
State University, with collaborators in OH, MI, IA, MN, NE, and ND. The
primary goal of the project is to analyze farmer data (yield, management
practices and associated costs) in fields located across the
North-Central US. Our primary focus is on increased profitability
through improved knowledge of yield-limiting factors and best management
practices.
There are two major segments of this project:
  
-    The production survey available
    [here](https://survey123.arcgis.com/share/4bacfb5607d147ac80c2fe282ad7206a)
 

-    Intensive field scouting across several states (more info
    [here](https://coolbean.info/soybean-research/data-driven-knowledge/))

All data collected will be kept strictly confidential.
 
